Data Management and Domain Adjusting Strategies for Implementing Parallel SPH Method in JPUE Simulation

### 2016-01-08 Paper for submission.tex
last commit

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Zhixuan Cao, Abani Patra}
\IEEEauthorblockA{Department of MAE \\%Mechanical and Aerospace Engineering
 The University at Buffalo\\
 Buffalo, New York 14260\\
Email: zhixuanc@buffalo.edu, \\ abani@buffalo.edu}
\and
\IEEEauthorblockN{Matthew Jones}
\IEEEauthorblockA{Center for Computational Research\\%Computer Science and Engineering
The University at Buffalo\\
Buffalo, New York 14260\\
Email: jonesm@buffalo.edu}
\and
\IEEEauthorblockN{Jaroslaw Zola}
\IEEEauthorblockA{Department of CSE\\
The University at Buffalo\\
Buffalo, New York 14260\\
Email:jzola@buffalo.edu}
}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Zhixuan Cao, Abani Patra}
\IEEEauthorblockA{Department of MAE \\%Mechanical and Aerospace Engineering
 The University at Buffalo\\
 Buffalo, New York 14260\\
Email: zhixuanc@buffalo.edu,\\abani@buffalo.edu}
\and
\IEEEauthorblockN{Matthew Jones}
\IEEEauthorblockA{Center for Computational Research\\%Computer Science and Engineering
The University at Buffalo\\
Buffalo, New York 14260\\
Email: jonesm@buffalo.edu}
\and
\IEEEauthorblockN{Jaroslaw Zola}
\IEEEauthorblockA{Department of CSE\\
The University at Buffalo\\
Buffalo, New York 14260\\
Email: jzola@buffalo.edu}
}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass
